### 2016-06-21 paper/numerical_experiments.tex
stash paper progress

In the previous examples, while the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time. In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI. In Section~\ref{sec:setup3D} we describe the setup of the models and their inverse problems, and in Section~\ref{sec:ref3D} we describe the results of applying Algorithm~\ref{alg:refSeries} to this pair of models.

>>>>

In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time. In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI. In Section~\ref{sec:setup3D} we describe the setup of the models and their inverse problems, and in Section~\ref{sec:ref3D} we describe the results of applying Algorithm~\ref{alg:refSeries} to this pair of models.

%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:setup3D}
%------------------------------------------------------------%

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-3}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

The low-fidelity model,
%
\begin{equation}
\nabla\cdot(n\vec{V}u - nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
\end{equation}
%
differs in the removal of both the reaction term and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$. The boundary conditions remain unchanged. As in the previous examples in Section~\ref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where (\ref{eq:HFeq3D}) and (\ref{eq:LFeq3D}) are solved, respectively. The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a domain twice the length in the $x_1$ and $x_2$ directions. The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}. We again require regularization, and use the regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.3\textwidth]{placeholder.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet is small enough to not require stabilization.

%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D}
%------------------------------------------------------------%
